\ttitle

### 2016-06-05 Appendices/AppendixAccessDatabase.tex
Grammar correction in Appendix 1

The RealLink for Windows (RFW, http://www.nps-reality.com/reallink) application used at Glasgow Royal Infirmary allowed access form VBA via Dynamic Data Exchange. This was used to collect and parse laboratory results for preoperative and postoperative blood results efficiently and without error.

>>>>

The RealLink for Windows (RFW, http://www.nps-reality.com/reallink) application used at Glasgow Royal Infirmary allowed access from VBA via Dynamic Data Exchange. This was used to collect and parse laboratory data for preoperative and postoperative blood tests efficiently and without error.
